DeepSphere: an efficient graph-based spherical CNN

### 2019-09-04 main.tex
affiliations

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review. 
\author{Michaël Defferrard, Martino Milani, Frédérick Gusset,  Nathanaël Perraudin \thanks{ Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

>>>>

\author{Michaël Defferrard, Martino Milani \& Frédérick Gusset \\
Institute of Electrical Engineering, EPFL, Lausanne, Switzerland \\
\texttt{\{michael.defferrard,martino.milani,frederick.gusset\}@epfl.ch}
\AND
Nathanaël Perraudin \\
Swiss Data Science Center (SDSC), Zurich, Switzerland \\
\texttt{nathanael.perraudin@sdsc.ethz.ch}
}
